D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling

### 2025-06-29 doc/article/article.tex

\usepackage{graphicx}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{cite}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algorithmic}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=50pt]{templates.png}
	\caption{An example of hand-picked template with SIFT descriptors.}
	\label{fig:templates}
\end{figure}

@@

\section{Arrow-Net}
\label{arrow-net}

This second approach for determining an arrow's orientation was inspired by UNet \cite{unet}. The core idea was to segment an arrow's bounding box, and to use a specific CNN to try and determine the arrow's head point and the arrow's tail point.

\begin{table}[htbp]
	\centering
	\caption{ArrowNet Architecture Details}
	\label{tab:arrownet}
	\begin{tabular}{|l|l|l|l|l|}
		\hline
		\textbf{Stage} & \textbf{Layer} & \textbf{Input Shape} & \textbf{Output Shape} & \textbf{Operations} \\
		\hline
		\multirow{3}{*}{Encoder} 
		& Encoder1 & $(B, 1, 256, 256)$ & $(B, 32, 256, 256)$ & Double Conv Block \\
		& MaxPool & $(B, 32, 256, 256)$ & $(B, 32, 128, 128)$ & $2 \times 2$ MaxPooling \\
		& Encoder2 & $(B, 32, 128, 128)$ & $(B, 64, 128, 128)$ & Double Conv Block \\
		\hline
		Bottleneck 
		& MaxPool + Bottleneck & $(B, 64, 128, 128)$ & $(B, 128, 64, 64)$ & MaxPool + Double Conv \\
		\hline
		\multirow{4}{*}{Decoder}
		& Upsampling2 & $(B, 128, 64, 64)$ & $(B, 64, 128, 128)$ & Transpose Conv Block \\
		& Skip + Decoder2 & $(B, 128, 128, 128)$ & $(B, 64, 128, 128)$ & Concat + Double Conv \\
		& Upsampling1 & $(B, 64, 128, 128)$ & $(B, 32, 256, 256)$ & Transpose Conv Block \\
		& Skip + Decoder1 & $(B, 64, 256, 256)$ & $(B, 32, 256, 256)$ & Concat + Double Conv \\
		\hline
		Output & Output Conv & $(B, 32, 256, 256)$ & $(B, 3, 256, 256)$ & $1 \times 1$ Convolution \\
		\hline
	\end{tabular}
\end{table}

>>>>

\usepackage{graphicx}
\usepackage{multirow}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{cite}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algorithmic}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=50pt, height=60pt]{templates.png}
	\caption{An example of hand-picked template with SIFT descriptors.}
	\label{fig:templates}
\end{figure}

@@

\section{ArrowNet}
\label{arrow-net}

This second approach for determining an arrow's orientation was inspired by UNet \cite{unet}. The core idea was to segment an arrow's bounding box, and to use a specific CNN to try and determine the arrow's head point and the arrow's tail point. The downsampling-upsampling network is called \textbf{ArrowNet} and its specifics can be found in Table~\ref{table:arrownet}.

\begin{table}[htbp]
	\centering
	\caption{ArrowNet Architecture Details}
	\label{tab:arrownet}
	\begin{tabular}{|l|l|l|l|l|}
		\hline
		\textbf{Stage} & \textbf{Layer} & \textbf{Out Channels} & \textbf{Operations} \\
		\hline
		\multirow{3}{*}{Encoder} 
		& Encoder1 & $32$ & Double Conv Block \\
		& MaxPool & $32$ & $2 \times 2$ MaxPooling \\
		& Encoder2 & $64$ & Double Conv Block \\
		\hline
		Bottleneck 
		& MaxPool + Bottleneck & $128$ & MaxPool + Double Conv \\
		\hline
		\multirow{4}{*}{Decoder}
		& Upsampling2 & $64$ & Transpose Conv Block \\
		& Skip + Decoder2 & $64$ & Concat + Double Conv \\
		& Upsampling1 & $32$ & Transpose Conv Block \\
		& Skip + Decoder1 & $32$ & Concat + Double Conv \\
		\hline
		Output & Output Conv & $3$ & $1 \times 1$ Convolution \\
		\hline
	\end{tabular}
	\label{table:arrownet}
\end{table}
